\documentclass{article}

\usepackage{fullpage}

\title{Solutions to Chapter 10 of \emph{Cracking the Coding Interview}}
\author{Daniel Miller}
\date{}

\begin{document}
\maketitle





\section*{10.1}

Let $p$ be the probability of making a shot. The probability of making $2$ out 
of $3$ shots is $3p^2(1-p)+p^3 = -2p^3 + 3p^2$. We want to know when 
$-2p^3+3p^2>p$, or equivalently, $-2p^2+3p>1$. This simplifies to 
$(p-3/4)^2<1/16$, or equivalently, $|p-3/4|<1/4$. So we have a unique reason to 
play the second game whenever $p\in (1/2,1)$. When $p\in \{0,1/2,1\}$, the 
probability of winning is the same for both games. 





\section*{10.2}

We assume that the triangle is equilateral, and that the ants all walk at the 
same constant speed. Two ants will collide if and only if they start walking 
opposite directions around the triangle. So the probability we are looking 
for is $6/8 = 3/4$. 

If the ants are walking on a regular $n$-gon, then there are $2^n$ possible 
configurations of ``walking directions,'' only $2$ of which (all ants walking 
counterclockwise and all ants walking clockwise) result in no collisions. So 
the probability of collision in this case is $(2^n-2)/2^n = 1-2^{n-1}$. 





\section*{10.3}

Let $l_i$ be the line $a_i x + b_i y = c_i$, $i\in \{1,2\}$. Since the $l_i$ 
are lines, some coefficient is $\ne 0$. Divide the equations for both lines 
through by that nonzero coefficient. If the resulting equations are identical, 
clearly there is an intersection. Otherwise, they intersect if and only if they 
have distinct slopes. 





\section*{10.5}

The line through the centers of the squares. 





\end{document}
